Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of the Moran process for the Iterated Prisoner's Dilemma

### 2017-10-24 main.tex
Add more summary statistics.
Have also moved the images out to make room.
Add state number to appendix for FSM players
Note that this is not necessarily the smallest number of states. That in
itself is a harder problem.
Increase font of correlation heatmaps.

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies.}
    \label{fig:comparison_deterministic}
    % TODO DEEMED Unreadable: reduce number of images.
\end{figure}

@@

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies.}
    \label{fig:comparison_stochastic}
    % TODO DEEMED Unreadable: reduce number of images.
\end{figure}

@@

When $N=2$ the Moran process is effectively a measure of the distribution of relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. The top 16 (10\%) strategies are
shown in
Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:

@@

\begin{figure}[!hbtp]
    \begin{subfigure}{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/boxplot_2_invade.pdf}
        \caption{The fixation probabilities for \(N=2\)}
        \label{fig:boxplot_2}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\columnwidth}
        \scriptsize
        \centering
        \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
        % TODO Add more summary statistics to this measure
        \label{tbl:summary_top_2}
    \end{subfigure}
    \caption{Performance of strategies for \(N=2\).}
    % TODO Move the plot
    % TODO Explain this more (see comment about error bars)
\end{figure}

@@

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \input{tex/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \scriptsize
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \input{tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}%

@@

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_invade.pdf}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    % TODO Increase font
    \label{fig:correlation_coefficients}
\end{figure}

@@

% TODO Reduce font
% TODO Add number of states for FSMs
\section{List of players}\label{app:list_of_players}

\begin{enumerate}
    \input{tex/list_of_players.tex}
\end{enumerate}

>>>>

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies.}
    \label{fig:comparison_deterministic}
\end{figure}

@@

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textbf{stochastic} strategies.}
    \label{fig:comparison_stochastic}
\end{figure}

@@

When $N=2$ the Moran process is effectively a measure of the distribution of relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
probabilities for the strategies considered. The top 16 (10\%) strategies are
% TODO Fix (have removed plot)
shown in
Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:

@@

\begin{table}[!hbtp]
    \tiny
    \centering
    \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
    \label{tbl:summary_top_2}
    % TODO Explain this more (see comment about error bars)
\end{table}

@@

\begin{table}[!hbtp]
    \centering
    \tiny
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \input{tex/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \tiny
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \input{tex/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}%

@@

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/correlation_heatmap_invade.pdf}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{img/correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    \label{fig:correlation_coefficients}
\end{figure}

@@

\section{List of players}\label{app:list_of_players}

\footnotesize
\begin{enumerate}
    \input{tex/list_of_players.tex}
\end{enumerate}
